Continuous Reinforcement Learning

### 2018-06-22 magnitudes.tex

\paragraph{Directly learning the advantage function.}
Let the system be defined by a state- and action-driven stochastic
differential equation
\begin{equation}
s_{t+\deltat}=s_t+\deltat F(s_t,a_t)+\sqrt{\deltat}\mathcal{N}(0,C(s_t))
\end{equation}
where we assume that the covariance noise does not depend on $a_t$. (If
$a_t$ itself is noisy, this will produce noise on $F$, but this noise
would typically be of order $\deltat$ unless the noise on $a_t$ is of
order $1/\sqrt{\deltat}$.)

>>>>

\paragraph{Directly learning the advantage function.}
(See Kenji Doya, Reinforcement Learning in Continuous Space and Time,
Neural Comp.\ 2000.)
Let the system be defined by a state- and action-driven stochastic
differential equation
\begin{equation}
s_{t+\deltat}=s_t+\deltat F(s_t,a_t)+\sqrt{\deltat}\mathcal{N}(0,C(s_t))
\end{equation}
where we assume that the covariance noise does not depend on $a_t$. (If
$a_t$ itself is noisy, this will produce noise on $F$, but this noise
would typically be of order $\deltat$ unless the noise on $a_t$ is of
order $1/\sqrt{\deltat}$.)
